\toolname: Property-Based Testing for MPC Security

### 2023-11-03 paper/main.tex
tweaks to the test section

\section{Statistical testing for MPC insecurity}

\subsection{Test algorithm}

@@

We use the techniques from \cite{chalupka2018fast}
to directly test for conditional dependence without any static analysis of the subject protocol.

@@

\subsection{Theoretical issues}

@@

The usual trade-offs of significance testing apply.
Setting $\alpha$ too low will cause programs who's insecure-ness is only marginally discernible to the D-Trees
to pass the test.
Setting $\alpha$ higher will compromise one's certainty that a failing program truly is insecure.
There are three reasons why this is not a serious problem with the test, each worth considering as its own subtlety.

@@

Our Python script for actually performing the test consumes a stream of fixed-length bit vectors as a CSV.
Annotation of which columns are available in the real and ideal worlds is provided in the header.
The CSV is parsed and broken up as needed as a \texttt{pandas} dataframe.
The individulal ML models are instances of \texttt{sklearn.tree.DecisionTreeClassifier},
and they're trained in parallel with \texttt{joblib.Parallel}.
The D-Tree scores are inflated by $+1 \cdot 10^{-10}$ to avoid division-by-zero in the score-ratio,
and the score distributions are compared by \texttt{scipy.stats.wilcoxon}.

TODO: link to github or other archive?

>>>>

\section{\toolname: a Statistical Test for Security}

This section describes \toolname, our approach for using statistical independence testing to find security bugs in MPC protocols. The approach is based on the \emph{fast conditional independence test} proposed by Chalupka et al.~\cite{chalupka2018fast}.

\subsection{Conditional Independence Testing by Classification}

Chalupka et al.~\cite{chalupka2018fast} present a high-dimensional conditional independence test based on the observation that if $P(X | Y, Z) = P(X | Y)$ (i.e. $X$ and $Z$ are conditionally independent given $Y$), then $Y$ and $Z$ together will not be more useful for predicting $X$ than $Y$ alone. They leverage this observation to design a test based on training machine learning classifiers: one classifier predicts $X$ from both $Y$ and $Z$, while the other predicts $X$ from $Y$ alone. If the first classifier yields better test error than the second, then the conditional independence property likely does not hold.

\subsection{The \toolname Algorithm}

@@

We use the techniques from Chalupka et al.~\cite{chalupka2018fast}
to directly test for conditional dependence without any static analysis of the subject protocol.

@@

\subsection{Interpreting Test Results}

@@

The usual trade-offs of significance testing apply.
Setting $\alpha$ too low will cause programs whose insecure-ness is only marginally discernible to the D-Trees
to pass the test.
Setting $\alpha$ higher will compromise one's certainty that a failing program truly is insecure.
There are three reasons why this is not a serious problem with the test, each worth considering as its own subtlety.

@@

Our Python script for actually performing the test consumes a stream of fixed-length bit vectors as a CSV.
Annotation of which columns are available in the real and ideal worlds is provided in the header.
The CSV is parsed and broken up as needed as a \texttt{pandas} dataframe.
The individulal ML models are instances of \texttt{sklearn.tree.DecisionTreeClassifier},
and they're trained in parallel with \texttt{joblib.Parallel}.
The D-Tree scores are inflated by $+1 \cdot 10^{-10}$ to avoid division-by-zero in the score-ratio,
and the score distributions are compared by \texttt{scipy.stats.wilcoxon}.
Our implementation and the code to reproduce our experimental evaluation are available as open-source.\footnote{(Link removed for anonymous submission)}
